Measuring individual differences in the understanding of gaze cues

### 2022-04-13 paper/manuscript.Rmd

# Design of our balloon finding task
- face value of task (or maybe in intro already?)

## Stimuli
Our newly implemented task features an online game where children or adults are asked to search for a balloon. The events proceed as follows. An animated agent (a sheep, monkey, or pig) looks out of a window of a house. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. At all times, the agent’s gaze tracks the movement of the target. That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. While the distance of the target's flight depends on the final location, the target moves at a constant speed. Participants are then asked to locate the target’s destination: they respond by touching or clicking onto a position on the screen. Visual access to the target’s true location is manipulated by a hedge. Participants either have full, partial, or no visual access to the true target location. When partial or no information about the target location is accessible, participants are expected to use the agent’s gaze as a cue.

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects. Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec. The landing of the target is accompanied by a tapping sound. Once the target landed, the instructor's voice asks "Where is the balloon?". For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice. If no response got registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

## Trials
Trials differ in the amount of visual access that participants have to the final target position. Before the test trials start, we present four training trials during which participants familiarize themselves with selecting positions on the screen. In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon. In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location. They are then asked to click on the invisible balloon, i.e., the location where they saw the target land. In test trials, participants have no visual access to the target flight nor the end location. Participants are expected to use the agent’s gaze as a cue to locate the target. The first trial of each type comprises a voice-over description of the presented events. The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script). After these four training and audio guided trials, participants receive 15 test trials. The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.

## Study versions
We designed two study versions which can be chosen according to the researchers' need. The study versions differ in the final hiding place of the target and, consequently, on the outcome measure: there is a continuous hedge version and a discrete box version. Both versions use the same first training trial and then differ in the consecutive training and test trials. 
In the hedge version, participants have to indicate their estimated target location directly on a hedge (i.e., hedge version). 
Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant’s click.
In the discrete study version, the target lands in a box and participants are asked to click on the  box that hides the target. Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations. Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses. 
Note that in the test trials of both study versions, the target flight is covered by a hedge. In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location. In the box version, the hedge shrinks completely. The boxes then hide the target's final destination.

(ref:figlab1) **Study setup**. 
(a) Infrastructure for online testing. (i) Subjects aged 3 – 99+ can participate. Data collection can take place anywhere: at home, in kindergartens or research institutes. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers.
(b) Continuous hedge version of the balloon finding task. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. 
(c) Discrete box version of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

@@

## Implementation
Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. A great advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.
The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
We utilized the zero configuration bundler Parcel to enable a live server for debugging, easy imports and minified scripts in order to save data storage.
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. 
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The GreenSock Animation Platform [GSAP; @greensock2022gsap] library was used to animate the movement of single SVG elements. 
We use URL parameters to capture the participant's ID, language and study version. 
The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany. Data got automatically collected and safely stored on these in-house servers. If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device. For child samples, we upload safety copies of the already collected responses after the fourth test trial. In cases where children want to stop participation earlier, no responses get lost.

# Does the balloon finding task induce variation?
Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample. Furthermore, we were interested in how the data collection mode influences responses.

The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between May and October 2021.

@@

vali_adults <- vali %>%
  filter(ageInYears == 18) %>% 
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)), 
    female = ifelse(gender == "f", 1, 0),
  ) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```
## Participants
We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology. The in-person child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).

For our remote child sample, we recruited families on a voluntary basis via email from our institute's internal database. The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls). Children in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

In addition, we recruited a remote adult sample by advertising the study on *Prolific*. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour). *Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.

## Procedure
Children in our in-person sample were tested on a tablet in a quiet room in their daycare center. An experimenter accompanied the child and helped them navigate through the online study.

Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted. In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure. Then, caregivers were informed about data security and were asked for their informed consent. They were asked to enable the sound and seat their child centrally in front of their device. Before the study started, families were instructed how to setup their webcam and enable the recording permissions. We stressed that caregivers should not help their children. Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
Depending on the participant's device, the website automatically presented the hedge or box version of the study. For families that used a tablet with touchscreen, the hedge version was shown. Here, children could directly click on the touchscreen themselves to indicate where the target is. For families that used a computer without touchscreen, the website presented the box version of the task. We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse. Therefore, we asked children to point to the screen, while caregivers were  asked to act as the "digital finger" of their children and click on the indicated box.

Our adult sample participated remotely without supervision.

All participants received 15 test trials that were displayed as described above. In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.

@@

For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a lognormal distribution. 
For the box version, the model predicted correct responses (0/1) using a Bernoulli distribution with a logit link function.
We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.

## Results
(ref:figlab2) **Measuring interindividual variation**. 
(a) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Internal consistency (odd-even split) in hedge child sample. (c) Internal consistency in hedge adult sample. (d) Test-retest reliability in hedge child sample. (e) Test-retest reliability in hedge adult sample.
(f) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(g) Internal consistency (odd-even split) in box child sample. (h) Internal consistency in box adult sample. (i) Test-retest reliability in box child sample. (j) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r.* 
Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small data points show the mean performance for each subject. Shape of data points represents data collection mode: opaque round circles stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection. Color of data points represent each age group (binned by year).

@@

We captured a developmental trajectory of gaze cue understanding: with increasing age, participants got more and more accurate in locating the target. In the hedge version, children's click imprecision droped with age, while, congruently, the proportion of correct responses increased in the box version (see Figure 2 A and F). Most participants in the box version performed above chance level. By the end of their sixth year of life, children came close to the adult's proficiency level. We found interindividual variation across study versions and age groups. For instance, this can be seen in that some three-year-olds were more precise in their responses than some five-year-olds.

@@

Our GLMM analysis corroborated the effects of age and data collection mode that we already identified by visual inspection: in the hedge version, we found an estimate of age of `r fixef(mAgeHedge)["age", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and an estimate of data collection mode of `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]). 
In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]). Note that the effect of data collection appears to be present, but confidence intervals are wide.

>>>>

# Task design
- face value of task (or maybe in intro already?)

## Stimuli
Our newly implemented task features an online game where children or adults are asked to search for a balloon. The events proceed as follows (see Figure \@ref(fig:fig1)B and C). An animated agent (a sheep, monkey, or pig) looks out of a window of a house. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. At all times, the agent’s gaze tracks the movement of the target. That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. While the distance of the target's flight depends on the final location, the target moves at a constant speed. Participants are then asked to locate the target: they respond by touching or clicking on the screen. Visual access to the target’s true location is manipulated by a hedge. Participants either have full, partial, or no visual access to the true target location. When partial or no information about the target location is accessible, participants are expected to use the agent’s gaze as a cue.

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects. Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec. The landing of the target is accompanied by a tapping sound. Once the target landed, the instructor's voice asks "Where is the balloon?". For confirming the participant's click, a short plop sound plays and a small orange circle appears at the location of choice. If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

## Trials
Trials differ in the amount of visual access that participants have to the final target position. Before the test trials start, participants complete four training trials during which they familiarize themselves with clicking the screen. In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon. In the second and third training trials, participants have partial access: they witness the target flight but cannot see the target's end location. They are then asked to click on the hidden balloon, i.e., the location where they saw the target land. In test trials, participants have no visual access to the target flight or the end location. Participants are expected to use the agent’s gaze as a cue to locate the target. The first trial of each type comprises a voice-over description of the presented events. The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script). After the four training trials, participants receive 15 test trials. The complete sequence of four training trials and 15 test trials can be easily completed within 5-10 minutes.

## Study versions
We designed two study versions which differ in the final hiding place of the target and, consequently, on the outcome measure: a *hedge version* (continuous) and a *box version* (discrete). Both versions use the same first training trial and then differ in the consecutive training and test trials. 
In the hedge version, participants have to indicate their estimated target location directly on a hedge. Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant’s click.
In the box version, the target lands in a box and participants are asked to click on the  box that hides the target. Researchers have the choice how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations. Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses. 
Note that in the test trials of both versions, the target flight is covered by a hedge. In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location. In the box version, the hedge shrinks completely. The boxes then hide the target's final destination (see Figure \@ref(fig:fig1)B and C).

(ref:figlab1) **Study setup**. 
(A) Infrastructure for online testing. (i) Subjects aged 3 – 99+ can participate. Data collection can take place anywhere: online, in kindergartens or research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers.
(B) Hedge version (continuous) of the balloon finding task. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. 
(C) Box version (discrete) of the balloon finding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

@@

## Implementation [m: das vll zuerst - vor der Beschreibung der versionen]
Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. An advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

The web-app was programmed in `JavaScript` (ECMAScript 2015, i.e., ES6), `HTML5`, `CSS` and `PHP`. For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene. The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording. These files can either be sent to a server or downloaded to the local device.

# Individual differences
Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample. Furthermore, we were interested in how the data collection mode influences responses.

Methods, sample size and analysis were pre-registered: https://osf.io/snju6 (child sample) and https://osf.io/r3bhn (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between May and October 2021.

@@

vali_adults <- vali %>%
  filter(ageInYears == 18) %>% 
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)), 
    female = ifelse(gender == "f", 1, 0),
  ) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```
## Participants
We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig, Germany. The in-person child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).

For our remote child sample, we recruited families via an internal database. The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls). Children in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via *Prolific*. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

## Procedure
Children in our in-person sample were tested on a tablet in a quiet room in their kindergarten. An experimenter guided the child through the study. Children in the remote sample received a personalized link to the study website and families could participate at any time or location they wanted. In the beginning of the online study, families were invited to enter our "virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure. Then, caregivers were informed about data security and were asked for their informed consent. They were asked to enable the sound and seat their child centrally in front of their device. Before the study started, families were instructed how to setup their webcam and enable the recording permissions. We stressed that caregivers should not help their children. Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves.
Depending on the participant's device, the website automatically presented the hedge or box version of the study. For families that used a tablet with touchscreen, the hedge version was shown. Here, children could directly click on the touchscreen themselves to indicate where the target is. For families that used a computer without touchscreen, the website presented the box version of the task. We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse. Therefore, we asked children to point to the screen, while caregivers were asked to act as the "digital finger" of their children and click on the indicated box.

All participants received 15 test trials. In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.

@@

For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution. For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function. We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.

## Results
(ref:figlab2) **Measuring interindividual variation**. 
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r*. [m: die regressions linie ist ein smoothed mean based on liner model - guck einfach mal ?geom_smooth] 
Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small points show the mean performance for each subject. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection. Color of data points denotes age group.

@@

We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target. In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure 2 A and F [m: siehe oben wie man auf die figures verweist]). Most participants in the box version performed above chance level. By the end of their sixth year of life, children came close to the adult's proficiency level. Most impoertantly, however, we found subtantial interindividual variation across study versions and age groups. For example, some three-year-olds were more precise in their responses than some five-year-olds [m: jetzt noch was zu den erwachsenene - sagen ,dass da auch variation ist; weniger als bei den kindern, but still].

@@

Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, we the estimates for age of ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were reliably different from zero [m: so würde ich alle estiamtes berichten. also sagen ob positive oder negative und ob veschieden von 0 oder nicht]. 
In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]). Note that the effect of data collection appears to be present, but confidence intervals are wide [m: das präziser - positive effect, but nor reliably different from 0 oder so].

## Discussion
Our task induced interintidivudal variation in both adults and children. With increasing age, participants got more and more precise in locating the target. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This illustrates the flexibility of the task.

# Internal consistency and retest reliability
